Modal type theory based on the intuitionistic epistemic logic

### 2018-01-17 article.tex
added SN proof

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{dsfont}
\usepackage[all, 2cell]{xy}
\usepackage[all]{xy}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{defin}{Definition}
\newtheorem{ex}{Example}
\newtheorem{col}{Corollary}
\newtheorem{con}{Convention}
\usepackage{listings} 		% for source code
\date{}
\title{Modal type theory based on the intuitionistic epistemic logic}

@@

@@

@@

@@

@@

    \bibitem{ModalK1} Kakutani Y. (2007) Call-by-Name and Call-by-Value in Normal Modal Logic. In: Shao Z. (eds) Programming Languages and Systems. APLAS 2007. Lecture Notes in Computer Science, vol 4807. Springer, Berlin, Heidelberg
  \end{thebibliography}

>>>>

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{dsfont}
\usepackage[all, 2cell]{xy}
\usepackage[all]{xy}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{defin}{Definition}
\newtheorem{ex}{Example}
\newtheorem{col}{Corollary}
\newtheorem{con}{Consequence}
\usepackage{listings} 		% for source code
\date{}
\title{Modal type theory based on the intuitionistic epistemic logic}

@@

  Let us show the next simple observation, which immeadelty follows from the previous definition.

    If $M \rightarrow_{\beta \eta} N$, then ${\bf pure \:} M \rightarrow_{\beta \eta} {\bf pure \:} N$.
  \end{lemma}

@@

  Strong normalization for ${\bf IK}$ is proved in \cite{Abe} \cite{ModalK}. So we consider simply typed lambda calculus with ${\bf K}_I$ rule and show that $\lambda_{\to, \times} + {\bf K}_I$ is strongly normalizable.

@@

  \begin{proof}
    $ $

    We build the subset of strongly normalazing terms and show that an arbitrary term belongs to this subset.

    \begin{defin} The set of strongly computable terms for every type $T \in \mathbb{T_{\bf K}}$.
      \begin{itemize}
        \item Let $A \in \mathbb{T}$, then $SC_A = \{ M : A \: | \: \text{$M$ is strongly normalizing}\}$;
        \item $SC_{A \to B} = \{ M : A \to B \: | \: \forall A \in SC_A, M N \in SC_B \}$;
        \item $SC_{A_1 \times A_2} = \{ M : A \times B \: | \: \pi_i M \in SC_{A_i}, i \in \{ 1, 2 \} \}$;
        \item $SC_{{\bf K}A} = \{ {\bf pure \:} M : {\bf K}A \: | \: M \in SC_A \}$
      \end{itemize}
    \end{defin}

    Strong normalization proof reduces to the proof of the next lemma:

      i) If $M \in SC_A$, then $M$ is stronly normalizing;

      ii) If $M \rightarrow_{\beta} M^{'}$ and $M \in SC_A$, then $M^{'}$;

      iii) Let $M \rightarrow_{\beta} M^{'}$ and $M^{'} \in SC_A$, then, if $M$ is a neutral term, then $M \in SC_A$.

      iv) Let $x_1 : A_1,\dots,x_n : A_n \vdash M : B$ and $\forall i \in \{ 1,\dots,n\}, N_i \in SC_{A_i}$, then $M [\vec{x} := \vec{N}] \in SC_B$.
    \end{lemma}

    \begin{proof}
      $ $

      i)

      The base case follows from the definition.

      Let us consider case with $SC_{{\bf K}A}$.
      If ${\bf pure \:} M \in SC_{{\bf K}A}$, then $M \in SC_A$ and $M$ is strongly normalizible.
      So ${\bf pure \:} M$ is strongly normalizible, otherwise there would be an infinite reduction path in ${\bf pure \:} M$.

      ii)

      The base case is trivial.

      Let ${\bf pure \:} M \rightarrow_{\beta} {\bf pure \:} M^{'}$ and ${\bf pure \:} M \in SN_{{\bf K}A}$.
      By assumption, $M \in SN_A$ and $M \rightarrow_{\beta} M^{'}$, so $M^{'} \in SN_A$. Hence ${\bf pure \:} M^{'} \in SC_{{\bf K}A}$ by the first statement of the lemma.

      iii)

      The base case is trivial.

      Let ${\bf pure \:} M \rightarrow_{\beta} {\bf pure \:} M^{'}$ and ${\bf pure \:} M^{'} \in SN_{{\bf K}A}$.

      ${\bf pure \:} M^{'}$ is a neutral by the definition. By assumption $M$ is a strongly normalizing. So ${\bf pure\:} M$ is a strongly normalizing by the first part of the current lemma.

      iv)

      Let $x_1 : A_1,\dots,x_n : A_n \vdash {\bf pure \:} M : {\bf K}A$ and $\forall i \in \{ 1,\dots,n\}, N_i \in SC_{A_i}$.

      By generation $x_1 : A_1,\dots,x_n : A_n \vdash M : A$ and by assumption $M [\vec{x} := \vec{N}] \in SC_B$.

      Hence, by the first part of lemma, ${\bf pure \:} (M [\vec{x} := \vec{N}]) \in SC_{{\bf K}B}$.
    \end{proof}

    \begin{col}
      $ $

      Let $\vdash N : A$, then $N$ is strongly normalizing.
    \end{col}

    \begin{proof}
      $ $

    If $\vdash N : A$, then $N \in SC_A$, hence $N$ is strongly normalizing.
    \end{proof}

@@

\begin{proof}
$ $
Straightforwardly follows from two previous lemmas.
\end{proof}

@@

  \bibitem{ModalK1} Kakutani Y. (2007) Call-by-Name and Call-by-Value in Normal Modal Logic. In: Shao Z. (eds) Programming Languages and Systems. APLAS 2007. Lecture Notes in Computer Science, vol 4807. Springer, Berlin, Heidelberg

  \bibitem{Abe} T. Abe. Completeness of modal proofs in first-order predicate logic. Computer Software, JSSST Journal, 24:165 -- 177, 2007.
  \end{thebibliography}
